---
title: "Chapter 6"
output: html_document
date: '2023-06-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 6.1
##1


With the following vector defined: foo <-c(13563, -14156, -14319, 16981, 12921, 11979, 9568, 8833, -12968, 8133)

Output the elements, that when foo is raised to the power 75, are NOT infinite.
```{r}
foo <-c(13563, -14156, -14319, 16981, 12921, 11979, 9568, 8833, -12968, 8133)
foo[is.finite(foo^75)]
```

##2

With the following vector defined: foo <-c(13563, -14156, -14319, 16981, 12921, 11979, 9568, 8833, -12968, 8133)

Output all the elements from foo, except those that result in negative infinity when raised to a power of 75

```{r}
foo[!(is.infinite(foo^75)&foo^75<0)]
```


##3

With the following matrix defined "bar":


```{r}
bar <- matrix(
    c(77875.40,-35466.25,-39803.81, 27551.45, -73333.85, 55976.34, 
      23764.30, 36599.69, 76694.82, -36478.88, -70585.69, 47032.00),
    nrow = 3, 
    ncol = 4
)
bar
```

Identify the coordinate-specific indexes of the entries of "bar" that are NaN when you raise "bar" to the power of 65 and divide by infinity.
```{r}
which(is.nan(bar^65 / Inf), arr.ind = TRUE)
```

##4

With the following matrix defined "bar":

```{r}
bar
```

Return the values in "bar" that are NOT NaN when "bar" is raised to a power of 67 and infinity is added to the result.
```{r}
!is.nan(bar^67 + Inf)
```

##5

With the following matrix defined "bar":

```{r}
bar
```

Identify those values in "bar" that are either negative infinity OR finite when you raise "bar" to a power of 67

```{r}
bar[(is.infinite(bar^67) & bar^67 < 0) | is.finite(bar^67)]
```

# 6.2

## 6
With the following vector defined. What is its length?

foo <- c(4.3, 2.2, NULL, 2.4, NaN, 3.3, 3.1, NULL, 3.4, NA)
```{r}
foo <- c(4.3, 2.2, NULL, 2.4, NaN, 3.3, 3.1, NULL, 3.4, NA)
length(foo)
```

## 7
With the following vector defined. 

foo <- c(4.3, 2.2, NULL, 2.4, NaN, 3.3, 3.1, NULL, 3.4, NA)

What will the following return?
```{r}
which(x = is.na(x = foo))
```

##8

With the following vector defined. 

foo <- c(4.3, 2.2, NULL, 2.4, NaN, 3.3, 3.1, NULL, 3.4, NA)

What will the following return?
```{r}
is.null(x = foo)
```

##9

With the following vector defined. 

foo <- c(4.3, 2.2, NULL, 2.4, NaN, 3.3, 3.1, NULL, 3.4, NA)

What will the following return?
```{r}
is.na(x = foo[8])+ 4 / NULL
```

##10

With the following list defined: Alist <- list(c(7, 7, NA, 3, NA, 1, 1, 5, NA))

Name the first element of the list "alpha"
```{r}
Alist <- list(c(7, 7, NA, 3, NA, 1, 1, 5, NA))
names(Alist) <- c("alpha")
```

##11

With the following list defined:

```{r}
Alist
```


Confirm that there is no item in the list named "beta"
```{r}
any(names(Alist) == "beta")
```

##12

With the following list defined:

```{r}
Alist
```

Create another member of the list named "beta". This new member should have all the positions of NAs from the "alpha" members.
```{r}
Alist$beta <- which(is.na(Alist$alpha))
```

#6.3

##13

```{r}
foo <- array(data = 1:36, dim = c(3, 3, 4))
class(foo)
bar <- as.vector(foo)
class(bar)
baz <- as.character(bar)
class(baz)
qux <- as.factor(baz)
class(qux)
quux <- bar + c(-0.1, 0.1)
class(quux)
```


## 14

What are three ways to get the dimensions of the matrix "Neo" defined as:

```{r}
Neo <- matrix(data = 1:36, nrow = 4, ncol = 9, byrow = TRUE)
dim(Neo)
attr(x = Neo, which = "dim")
attributes(Neo)$dim
```

## 15

With the matrix "Trinity" defined:
```{r}
Trinity <- matrix(data = 2:13, nrow = 3, ncol = 4)
Trinity
```

convert the contents into:

```{r}
as.character(Trinity)
```

## 16
With the following matrix "mat" defined:
```{r}
mat <- matrix(c(34, 23, 33, 42, 41, 0, 1, 1, 0, 0, 1, 2, 1, 1, 2), nrow = 5, ncol = 3)
mat
```

Coerce the matrix into a dataframe named "df":
```{r}
df <- data.frame(mat)
```

## 16
With the following dataframe "df" defined:
```{r}
df
```
Coerce the second column as logical:
```{r}
df[,2] <- as.logical(df[,2])
```

## 17
With the following dataframe "df" defined:
```{r}
df
```

Coerce the 3rd column as factor
```{r}
df[,3] <- as.factor(df[,3])
```

