---
title: "Chapter 2"
output: html_document
date: '2023-06-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 2.1 R for Basic Math

### 2.1.1 Arithmetic



### 2.1.2 Logarithms and Exponentials
Find the base 3 logarithm of 243:
```{r}
log(x = 243, base = 3)
```

Find the value of \(e^3\):
```{r}
exp(x = 3)
```

Find the natural log of 20.08554:
```{r}
log(x = 20.08554)
```

### 2.1.3 E-Notation

## Exercise 2.1
Calculate the square root of half of the average of the numbers: 25.2, 15, 16.44, 15.3, 18.6
```{r}
vec <- c(25.2, 15, 16.44, 15.3, 18.6)
```



```{r}
sqrt(mean(c(25.2, 15, 16.44, 15.3, 18.6)) / 2)
```

Find the \(log_e(0.3)\)
```{r}
log(x = 0.3, base = exp(1))
```


Type the exponential notation of the number: -0.0005
```{r}
-5e-4
```

Type the command to create the following output:
```{r}
rep(x = c(3, 62, 8.3), times = 3, each = 2)
```

Create 'my_seq' and store a sequence of values from 5 to -11 that progresses in steps of 0.3

```{r}
my_seq <- seq(from = 5, to = -11, by = -0.3)
```

Create 'my_seq' and store a sequence of values from 5 to -11 that progresses in steps of 0.3, but have it in reverse order

```{r}
(my_seq <- sort(x = seq(from = 5, to = -11, by = -0.3)))
```

Create 'Z' as the repeat of the vector c(-1, 3, -5, 7, -9) twice, with each element repeated 10 times:
```{r}
Z <- rep(c(-1, 3, -5, 7, 9), times = 2, each = 10)
```

Display the vector 'Z' from largest to smallest.
```{r}
sort(Z, decreasing = TRUE)
```


Create a vector which has the following items in order:

- Sequence of integers from 6 to 12
- A threefold repetition of the value 5.3
- The number -3
- A sequence of nine values starting at 102, decreasing by 1/3
```{r}
c(seq(6, 12),rep(5.3, times = 3), -3, seq(102, by = -1/3, length = 9))
```

The 'my_vec' vector is defined as (2, 0.5, 1, 2, 0.5, 1, 2, 0.5, 1). Convert it to a vector of only 1s, using a vector of length 3.
```{r}
my_vec <- c(2, 0.5, 1, 2, 0.5, 1, 2, 0.5, 1)
my_vec / c(2, 0.5, 1)
```


Use the vector c(2, 4, 6) and the vector c(1, 2) in conjunction with 'rep' and * to produce the vector c(2, 4, 6, 4, 8, 12)
```{r}
rep(c(1,2), times = 1, each = 3) * c(2, 4, 6)
```

The vector 'v' is defined as (2, 4, 6, 4, 8, 12). Overwrite the middle 4 values of v with the values -0.1 and -100 recycled 2x in that order.
```{r}
v[2:5] <- rep(c(-0.1, -100), each = 2)
```

