---
title: "Chapter 3"
output: html_document
date: '2023-06-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1

What is the default argument for the "matrix" function which identifies the way in which it is loaded during definition?
byrow = FALSE

## 2
Fill a 2x3 matrix in column-wise fashion with vector 1, 2, 3, ..., 6 using all named attributes 

[for display only...no need to assign a variable]

```{r}
matrix(data = 1:6, nrow = 2, ncol = 3, byrow = FALSE)
```

##3

Create the following matrix using 2 vectors: 1:3 and 4:6

\[
\begin{bmatrix}
1 & 2 & 3 \\
4 & 5 & 6
\end{bmatrix}
\]



```{r}
rbind(1:3, 4:6)
```

##4

Create the following matrix using the 3 vectors: 1:2, 3:4, and 5:6

\[
\begin{bmatrix}
1 & 3 & 5 \\
2 & 4 & 6 \\
\end{bmatrix}
\]


[for display only...no need to assign a variable]
```{r}
cbind(1:2, 3:4, 5:6)
```

##5
The matrix A is defined as below. Type the command to extract the value 105.5

\[
A= \begin{bmatrix}
0.3 & 91.0 & -4.2 \\
4.5 & 0.1 & 8.2 \\
55.3 & 105.5 & 27.9
\end{bmatrix}
\]

```{r}
A <- matrix(c(0.3, 4.5, 55.3, 91, 0.1, 105.5, -4.2, 8.2, 27.9), nrow = 3, ncol = 3)
A
```
```{r}
A[3,2]
```

##6
Extract the first row from A

\[
A= \begin{bmatrix}
0.3 & 91.0 & -4.2 \\
4.5 & 0.1 & 8.2 \\
55.3 & 105.5 & 27.9
\end{bmatrix}
\]
```{r}
A[1,]
```

##7
Select the 3rd column and 1st column of A (in that order)
\[
A= \begin{bmatrix}
0.3 & 91.0 & -4.2 \\
4.5 & 0.1 & 8.2 \\
55.3 & 105.5 & 27.9
\end{bmatrix}
\]
```{r}
A[,c(3,1)]
```

##8
Extract the diagonal of A

\[
A= \begin{bmatrix}
0.3 & 91.0 & -4.2 \\
4.5 & 0.1 & 8.2 \\
55.3 & 105.5 & 27.9
\end{bmatrix}
\]

```{r}
diag(x = A)
```

##9
Construct the 4x2 matrix "B" in row-wise fashion with the values: 4.3, 3.1, 8.2, 8.2, 3.2, 0.9, 1.6, 6.5 

[name ALL arguments]

\[
B= \begin{bmatrix}
4.3 & 3.1 \\
8.2 & 8.2 \\
3.2 & 0.9\\
1.6 & 6.5
\end{bmatrix}
\]

```{r}
B <- matrix(data = c(4.3, 3.1, 8.2, 8.2, 3.2, 0.9, 1.6, 6.5), nrow = 4, ncol = 2, byrow = TRUE)
```

##10
The matrix "B" is a 4x2 matrix. Show the dimensions of the matrix B after removing the first row. [Use a function]

\[
B= \begin{bmatrix}
4.3 & 3.1 \\
8.2 & 8.2 \\
3.2 & 0.9\\
1.6 & 6.5
\end{bmatrix}
\]
```{r}
dim(B[-1,])
```

##11
The matrix "B" is a 4x2 matrix. Overwrite the 2nd column of B with the same column, but sorted from smallest to largest

\[
B= \begin{bmatrix}
4.3 & 3.1 \\
8.2 & 8.2 \\
3.2 & 0.9\\
1.6 & 6.5
\end{bmatrix}
\Longrightarrow
\begin{bmatrix}
4.3 & 0.9 \\
8.2 & 3.1 \\
3.2 & 6.5\\
1.6 & 8.2
\end{bmatrix}
\]
```{r}
B[,2] <- sort(x = B[,2], decreasing = FALSE)
B
```
##12

The following 2 matrices are defined:

\[
  A = 
\begin{bmatrix}
1 \\
2 \\
7
\end{bmatrix}\;\;
B = 
\begin{bmatrix}
3 \\
4 \\
8
\end{bmatrix}
\]

Type the command to execute the following:

\(A^{\intercal} \cdot B\)

```{r}
A <- matrix(c(1, 2, 7))
B <- matrix(c(3, 4, 8))
t(A) %*% B
```

##13
If the following matrix A is defined. Type the command to execute the following: \(A^{-1} \cdot A - I_4\) thus confirming the answer is a 4x4 matrix of all 0s.

\[
A = 
\begin{bmatrix}
2 & 0 & 0 & 0 \\
0 & 3 & 0 & 0 \\
0 & 0 & 5 & 0 \\
0 & 0 & 0 & -1
\end{bmatrix}
\]

```{r}
A <- diag(x = c(2, 3, 5, -1))
solve(A) %*% A - diag(nrow = 4)
```

##14
Create a 3-D array (call it DRay) with six layers of a 4X2 matrix, filled with a decreasing sequence of values between 4.8 and 0.1 of the appropriate length. [Name all arguments]

```{r}
DRay <- array(data = seq(from = 4.8, to = 0.1, length = 48), dim = c(4, 2, 6))
```
##15
There is a 3-D array called DRay with six layers of a 4X2 matrix. Extract 4th and 1st-row elements, in that order, of the second column only of all layers and store as 'sDRay'.
```{r}
sDRay <- DRay[c(4,1),2,]
```

##16
We have a 2x6 matrix defined named 'sDRay' (from previous exercises). Use a fourfold repetition of the second row to fill a new array of dimensions 2x2x2x3.

```{r}
array(data = rep(sDRay[2,], 4), dim = c(2, 2, 2, 3))
```

##17
Create a new array called 'fiveLayer' comprised of the results of deleting the sixth layer of the 4x2x6 array called 'DRay'

```{r}
fiveLayer <- DRay[,,-6]
```

##18
There is a 4x2x5 dimension array named 'fiveLayer'. Overwrite the second and fourth row elements of the second column of layers 1, 3, and 5 with -99.
```{r}
fiveLayer[c(2,4),2,c(1, 3, 5)] <- -99
```

